---
title: "Abby-practice-code"
author: "Abby Robinson"
date: "7/12/2022"
output: html_document
---

Preliminary code for the Bamona project with Battus philenor data 

```{r}
library(curl)
b <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall21/KamilarAndCooperData.csv")
data <- read.csv(b, header = TRUE, sep = ",")
data
```


```{r}
library(curl)
b <- curl("https://raw.githubusercontent.com/butterfliesrcool/Bomona_Project/main/battus_philenor.csv")
battus <- read.csv(b, header = TRUE, sep = ",")
head(battus)
```
```{r}
length(battus$Longitude)
clean.battus <- na.omit(battus)
length(clean.battus$Longitude)
```


```{r}
library(sf)
battus <- st_as_sf(clean.battus, coords = c("Lat.Long", "Longitude"))
```

```{r}
q <- ggplot() + geom_sf(data = battus, color = "light pink", alpha = 0.5) + theme_bw()
q
```

```{r}
us <- c(left = -125, bottom = 25.75, right = -67, top = 49)
us
map <- get_stamenmap(us, zoom = 5, maptype = "toner-lite") %>% ggmap() 
map
#  Map tiles by Stamen Design, under CC BY 3.0. Data by OpenStreetMap, under ODbL.
```

NEXT STEP: Figure out how to load map of the US into R using ggmap and Google Maps API and plot the Battus coordinate data onto the map

Now, unfortunately, {agehabitatHR} does not yet allow for the use of {sf} objects. To use the spider monkey points in this package, we need to convert them to a spatial points object. We can do this by reimporting the dataframe and converting it to an {sp} object rather than an {sf} object:

```{r}
# Create a coordinate column, with both your X and Y values:

b <- curl("https://raw.githubusercontent.com/butterfliesrcool/Bomona_Project/main/battus_philenor.csv")
battus <- read.csv(b, header = TRUE, sep = ",")
clean.battus <- na.omit(battus)
xy <- clean.battus[, c("Lat.Long", "Longitude")]

# Create your Spatial Points dataframe:

library(sp)
battus.sp <- SpatialPointsDataFrame(coords = xy, data = clean.battus, proj4string = CRS("+proj=utm +zone=18 +south +datum=WGS84 +units=m +no_defs"))
```

```{r}
battus.sp.sf <- st_as_sf(battus.sp)

q <- ggplot() + geom_sf(data = battus.sp.sf, color = "light pink", alpha = 0.5) + theme_bw()
```
```{r}
library(adehabitatHR)
battus.mcp <- mcp(battus.sp, percent = 100)
battus.mcp ##the range estimate here doesn't really make sense, how can i incorporate specific data about the geography of the US to better inform range estimates? 
```
```{r}
# First, we'll convert our polygon into an {sf} object:
battus.mcp <- st_as_sf(battus.mcp)

# Now, let's map it:
mcp1 <- q + geom_sf(data = battus.mcp, color = "pink", fill = "pink", alpha = 0.3)
mcp1
```


```{r}
# First, we'll convert our polygon into an {sf} object:
battus.mcp <- st_as_sf(battus.mcp)

# Now, let's map it:
mcp1 <- q + geom_sf(data = battus.mcp, color = "pink", fill = "pink", alpha = 0.3)
mcp1
```
##Kernel Density Estimated Home Range
Another way of estimating the home range is to take into account how often certain parts of the home range are used based on the density of observation points in a particular area of that range. Such density estimates assume that the observation points represent a random sample of occupation points that are not biased by observer sampling. We might be wary of this method if, for example, all our observations were on the trail system. Here, however, we do appear to have a relatively unbiased sample.

In this case, we can try to get a kernel density estimate of the home range. Kernel density estimates essentially plot a smoothed curve over the density of points in a given geographic area (for an excellent, intuitive visual descriptor of the process, see this resource), which allows us to create a home range based on frequency of use rather than just a presence/absence MCP. Remember: although a kernel density estimator also uses presence data, absence is also considered to be data, as the density of points is a meaningful parameter.

```{r}
library(adehabitatHR)
battus_k100 <- kernelUD(battus.sp)
image(battus_k100)
```

```{r}
kern99 <- getverticeshr(battus_k100, percent = 99)
kern85 <- getverticeshr(battus_k100, percent = 85)

kern99 <- st_as_sf(kern99)
kern85 <- st_as_sf(kern85)
kern <- q + geom_sf(data = kern99, color = "pink", fill = "pink", alpha = 0.3) + 
    geom_sf(data = kern85, color = "salmon1", fill = "salmon1", alpha = 0.3)
kern
```


###Same thing, but with Limenitis and lets see if we can put both datasets on the same graph! 

```{r}
# Create a coordinate column, with both your X and Y values:

l <- curl("https://raw.githubusercontent.com/butterfliesrcool/Bomona_Project/main/limenitis_arthemis_astyanax.csv")
lim <- read.csv(l, header = TRUE, sep = ",")
clean.lim <- na.omit(lim)
xy <- clean.lim[, c("Lat.Long", "Longitude")]

# Create your Spatial Points dataframe:

library(sp)
lim.sp <- SpatialPointsDataFrame(coords = xy, data = clean.lim, proj4string = CRS("+proj=utm +zone=18 +south +datum=WGS84 +units=m +no_defs"))
```

```{r}
lim.sp.sf <- st_as_sf(lim.sp)

q <- ggplot() + geom_sf(data = lim.sp.sf, color = "light pink", alpha = 0.5) + theme_bw()
```
```{r}
library(adehabitatHR)
lim.mcp <- mcp(lim.sp, percent = 100)
lim.mcp ##the range estimate here doesn't really make sense, how can i incorporate specific data about the geography of the US to better inform range estimates? 
```
```{r}
# First, we'll convert our polygon into an {sf} object:
lim.mcp <- st_as_sf(lim.mcp)

# Now, let's map it:
mcp1 <- q + geom_sf(data = lim.mcp, color = "pink", fill = "pink", alpha = 0.3) + geom_sf(data = battus.mcp, color = "blue", fill = "blue", alpha = 0.3)
mcp1
```

```{r}
library(adehabitatHR)
lim_k100 <- kernelUD(lim.sp)
image(lim_k100)
```

```{r}
kern99 <- getverticeshr(lim_k100, percent = 99)
kern85 <- getverticeshr(lim_k100, percent = 85)

kern99 <- st_as_sf(kern99)
kern85 <- st_as_sf(kern85)
kern <- q + geom_sf(data = kern99, color = "pink", fill = "pink", alpha = 0.3) + 
    geom_sf(data = kern85, color = "salmon1", fill = "salmon1", alpha = 0.3)
kern
```
```{r}
# Google is weird in that their 'bounding box' (coordinates that set the
# boundary of the image we download) is in a fixed coordinate system, so we
# need to define a function to fix the 'bounding box' to be in our actual
# data projection of EPSG:32718:
ggmap_bbox <- function(map) {
    if (!inherits(map, "ggmap")) 
        stop("map must be a ggmap object")
    # Extract the bounding box (in lat/lon) from the ggmap to a numeric vector,
    # and set the names to what sf::st_bbox expects:
    map_bbox <- setNames(unlist(attr(map, "bb")), c("ymin", "xmin", "ymax", 
        "xmax"))
    
    # Coonvert the bbox to an sf polygon, transform it to 32718, and convert
    # back to a bbox (convoluted, but it works)
    bbox_32718 <- st_bbox(st_transform(st_as_sfc(st_bbox(map_bbox, crs = 4326)), 
        32718))
    
    # Overwrite the bbox of the ggmap object with the transformed coordinates
    attr(map, "bb")$ll.lat <- bbox_32718["ymin"]
    attr(map, "bb")$ll.lon <- bbox_32718["xmin"]
    attr(map, "bb")$ur.lat <- bbox_32718["ymax"]
    attr(map, "bb")$ur.lon <- bbox_32718["xmax"]
    map
}

# Use the function to change the coordinate system of the bounding box:
map <- ggmap_bbox(map)

p <- ggmap(map) + coord_sf(xlim = c(-76.18, -76.13), ylim = c(-0.63, -0.66), 
    crs = st_crs(32718)) + geom_sf(data = tbs_trails, inherit.aes = FALSE) + 
    geom_sf(data = tbs_rio, color = "dodgerblue", inherit.aes = FALSE) + geom_sf(data = d, 
    color = "light pink", alpha = 0.5, inherit.aes = FALSE)
```
