---
title: "abundance-by-county"
author: "Abby Robinson"
date: "10/4/2022"
output: html_document
---
Load Package Libraries
```{r}
library(curl)
library(sf)
library(ggplot2)
library(ggmap)
library(sp)
library(adehabitatHR)
library(cowplot)
library(googleway)
library(ggrepel)
library(ggspatial)
library(rnaturalearth)
library(rnaturalearthdata)
library(lubridate)
```

iNaturalist data 
```{r}
### battus 
b <- curl("https://raw.githubusercontent.com/butterfliesrcool/BAMONA/main/iNaturalist_battus_philenor_for_r.csv")
battus <- read.csv(b, header = TRUE, sep = ",")
head(battus)

length(battus$id) ### Sample size: 34,893
b <- subset(iNat.battus, select = c(id, observed_on, latitude, longitude, place_county_name, place_state_name, scientific_name) )
head(b)
battus <- na.omit(b)
length(battus$id) ### New sample size: 34,795
```

```{r}
##   limenitis 
l <- curl("https://raw.githubusercontent.com/butterfliesrcool/BAMONA/main/iNaturalist_limenitis_arthemis_astyanax.csv")
limenitis <- read.csv(l, header = TRUE, sep = ",")
head(limenitis)

length(limenitis$id) ### Sample Size: 20,908
l <- subset(limenitis, select = c(id, observed_on, latitude, longitude, place_county_name, place_state_name, scientific_name) )
head(l)
limenitis <- na.omit(l)
length(limenitis$id) ###New Sample Size:20,855
```

```{r}
##   polyxenes
p <- curl("https://raw.githubusercontent.com/butterfliesrcool/BAMONA/main/iNaturalist_papilio_polyxenes.csv")
polyxenes <- read.csv(p, header = TRUE, sep = ",")
head(polyxenes)

length(polyxenes$id) ### Sample Size: 58,735
p <- subset(polyxenes, select = c(id, observed_on, latitude, longitude, place_county_name, place_state_name, scientific_name) )
head(p)
polyxenes <- na.omit(p)
length(polyxenes$id) ###New Sample Size: 58,563
```

```{r}
##   troilus
t <- curl("https://raw.githubusercontent.com/butterfliesrcool/BAMONA/main/iNaturalist_papilio_troilus.csv")
troilus <- read.csv(t, header = TRUE, sep = ",")
head(troilus)

length(troilus$id) ### Sample Size: 25,174
t <- subset(troilus, select = c(id, observed_on, latitude, longitude, place_county_name, place_state_name, scientific_name) )
head(t)
troilus <- na.omit(t)
length(troilus$id) ###New Sample Size: 25,077
```

```{r}
##   glaucus
g <- curl("https://raw.githubusercontent.com/butterfliesrcool/BAMONA/main/iNaturalist_papilio_glaucus%20(version%201).xlsb.csv")
glaucus <- read.csv(g, header = TRUE, sep = ",")
head(glaucus)

length(glaucus$id) ### Sample Size: 66,657
g <- subset(glaucus, select = c(id, observed_on, latitude, longitude, place_county_name, place_state_name, scientific_name, morph) )
head(g)
glaucus <- na.omit(g)
length(glaucus$id) ###New Sample Size: 64,713

###### Separate only mimetic morphs 
glaucus <- subset(glaucus, morph == "black", drop = FALSE)
length(glaucus$id) ###Final Sample Size: 15,988
```

```{r}
##   diana 
d <- curl("https://raw.githubusercontent.com/butterfliesrcool/BAMONA/main/iNaturalist_speyeria_diana_edited%20-%20Sheet1.csv")
diana <- read.csv(d, header = TRUE, sep = ",")
head(diana)

length(diana$id) ### Sample Size: 657
d <- subset(diana, select = c(id, sex, observed_on, latitude, longitude, place_county_name, place_state_name, scientific_name) )
head(d)

diana <- na.omit(d)
length(diana$id) ###New Sample Size: 651

###### Separate only mimetic morphs 
diana <- subset(diana, sex == "f", drop = FALSE)
length(diana$id) ###Final Sample Size: 186
```

## use lubricate package to create column with just months from the dates 
```{r}
b.dates <- parse_date_time(battus$observed_on, "ymd")
b.months <- months(b.dates)
battus$months <- b.months
battus.summer <- subset(battus, months %in% c( "June", "July", "August"), drop = FALSE)
length(battus.summer$id) ### Sample Size: 13,939
```

```{r}
l.dates <- parse_date_time(limenitis$observed_on, "ymd")
l.months <- months(l.dates)
limenitis$months <- l.months
limenitis.summer <- subset(limenitis, months %in% c( "June", "July", "August"), drop = FALSE)
length(limenitis.summer$id) ### Sample Size: 13,787
```

```{r}
p.dates <- parse_date_time(polyxenes$observed_on, "ymd")
p.months <- months(p.dates)
polyxenes$months <- p.months
polyxenes.summer <- subset(polyxenes, months %in% c( "June", "July", "August"), drop = FALSE)
length(polyxenes.summer$id) ### Sample Size: 36,226
```

```{r}
t.dates <- parse_date_time(troilus$observed_on, "ymd")
t.months <- months(t.dates)
troilus$months <- t.months
troilus.summer <- subset(troilus, months %in% c( "June", "July", "August"), drop = FALSE)
length(troilus.summer$id) ### Sample Size: 18,617
```

```{r}
g.dates <- parse_date_time(glaucus$observed_on, "mdy")
g.months <- months(g.dates)
glaucus$months <- g.months
glaucus.summer <- subset(glaucus, months %in% c( "June", "July", "August"), drop = FALSE)
length(glaucus.summer$id) ### Sample Size: 11,650
```

```{r}
d.dates <- parse_date_time(diana$observed_on, "ymd")
d.months <- months(d.dates)
diana$months <- d.months
diana.summer <- subset(diana, months %in% c( "June", "July", "August"), drop = FALSE)
length(diana.summer$id) ### Sample Size: 104
```

```{r}
new.glau <- subset(glaucus.summer, select = c(id, observed_on, latitude, longitude, place_county_name, place_state_name, scientific_name, months) )

new.dia <- subset(diana.summer, select = c(id, observed_on, latitude, longitude, place_county_name, place_state_name, scientific_name, months) )

iNat.data <- rbind(battus.summer, limenitis.summer, polyxenes.summer, troilus.summer, new.glau, new.dia)
```

```{r}
abundance <- aggregate(x= iNat.data$scientific_name, by= list(iNat.data$place_state_name, iNat.data$place_county_name, iNat.data$scientific_name), FUN=length)
abundance #### there are 2,557 "zones" of comparison across the mimicry complex 

abundance$Location <- paste(abundance$Group.2, abundance$Group.1, sep = ", ")

abundance <- abundance[order(abundance$Location),]

abundance$Species <- abundance$Group.3
abundance$Sightings <- abundance$x

abundance <- subset(abundance, select = c(Location, Species, Sightings) )
abundance <- abundance[order(abundance$Sightings,decreasing=T),]
head(abundance)
```

```{r}
battus.abundance <- aggregate(x= battus.summer$scientific_name, by= list(battus.summer$place_state_name, battus.summer$place_county_name), FUN=length)

battus.abundance$Location <- paste(battus.abundance$Group.2, battus.abundance$Group.1, sep = ", ")

battus.abundance$Battus <- battus.abundance$x

bat <- subset(battus.abundance, select = c(Location, Battus) )
bat <- bat[order(bat$Battus,decreasing=T),]
head(bat)
```

```{r}
limenitis.abundance <- aggregate(x= limenitis.summer$scientific_name, by= list(limenitis.summer$place_state_name, limenitis.summer$place_county_name), FUN=length)

limenitis.abundance$Location <- paste(limenitis.abundance$Group.2, limenitis.abundance$Group.1, sep = ", ")

limenitis.abundance$Limenitis <- limenitis.abundance$x

lim <- subset(limenitis.abundance, select = c(Location, Limenitis) )
lim <- lim[order(lim$Limenitis,decreasing=T),]
head(lim)
```

```{r}
polyxenes.abundance <- aggregate(x= polyxenes.summer$scientific_name, by= list(polyxenes.summer$place_state_name, polyxenes.summer$place_county_name), FUN=length)

polyxenes.abundance$Location <- paste(polyxenes.abundance$Group.2, polyxenes.abundance$Group.1, sep = ", ")

polyxenes.abundance$Polyxenes <- polyxenes.abundance$x

pol <- subset(polyxenes.abundance, select = c(Location, Polyxenes) )
pol <- pol[order(pol$Polyxenes,decreasing=T),]
head(pol)
```

```{r}
troilus.abundance <- aggregate(x= troilus.summer$scientific_name, by= list(troilus.summer$place_state_name, troilus.summer$place_county_name), FUN=length)

troilus.abundance$Location <- paste(troilus.abundance$Group.2, troilus.abundance$Group.1, sep = ", ")

troilus.abundance$Troilus <- troilus.abundance$x

tro <- subset(troilus.abundance, select = c(Location, Troilus) )
tro <- tro[order(tro$Troilus,decreasing=T),]
head(tro)
```

```{r}
glaucus.abundance <- aggregate(x= new.glau$scientific_name, by= list(new.glau$place_state_name, new.glau$place_county_name), FUN=length)

glaucus.abundance$Location <- paste(glaucus.abundance$Group.2, glaucus.abundance$Group.1, sep = ", ")

glaucus.abundance$Glaucus <- glaucus.abundance$x

gla <- subset(glaucus.abundance, select = c(Location, Glaucus) )
gla <- gla[order(gla$Glaucus,decreasing=T),]
head(gla)
```

```{r}
diana.abundance <- aggregate(x= new.dia$scientific_name, by= list(new.dia$place_state_name, new.dia$place_county_name), FUN=length)

diana.abundance$Location <- paste(diana.abundance$Group.2, diana.abundance$Group.1, sep = ", ")

diana.abundance$Diana <- diana.abundance$x

dia <- subset(diana.abundance, select = c(Location, Diana) )
dia <- dia[order(dia$Diana,decreasing=T),]
head(dia)
```

```{r}
###merge is designed to work with two dataframes 
bl <- merge(bat, lim, all=TRUE)
pt <- merge(pol, tro, all=TRUE)
blpt <- merge(bl, pt, all=TRUE)
dg <- merge(dia, gla, all=TRUE)
all <- merge(blpt, dg, all=TRUE)
head(all)
```

```{r}
c <- curl("https://raw.githubusercontent.com/butterfliesrcool/BAMONA/main/county_area_data.csv")
county_area <- read.csv(c, header = TRUE, sep = ",")
head(county_area)
```

```{r}
county_area$Location <- paste(county_area$name, county_area$state, sep = ", ")
head(county_area)

county.area <- subset(county_area, select = c(Location, area_2010_square_km) )

abundance_and_area <- merge(all, county.area, all=FALSE)
abundance_and_area[is.na(abundance_and_area)] <- 0 ##Replace NAs with 0 
head(abundance_and_area)
#### Land Area Data Source: https://www.openintro.org/data/?data=county_complete

sums <- subset(abundance_and_area, select = -c(Location, area_2010_square_km) )
density <- rowSums(sums)

abundance_and_area$Species.Density <- density
abundance_and_area
```


```{r}
stnd_battus <- abundance_and_area$Battus/abundance_and_area$area_2010_square_km
abundance_and_area$Battus_per_sq_km <- stnd_battus

stnd_limenitis <- abundance_and_area$Limenitis/abundance_and_area$area_2010_square_km
abundance_and_area$Limenitis_per_sq_km <- stnd_limenitis

stnd_polyxenes <- abundance_and_area$Polyxenes/abundance_and_area$area_2010_square_km
abundance_and_area$Polyxenes_per_sq_km <- stnd_polyxenes

stnd_troilus <- abundance_and_area$Troilus/abundance_and_area$area_2010_square_km
abundance_and_area$Troilus_per_sq_km <- stnd_troilus

stnd_diana <- abundance_and_area$Diana/abundance_and_area$area_2010_square_km
abundance_and_area$Diana_per_sq_km <- stnd_diana

stnd_glaucus <- abundance_and_area$Glaucus/abundance_and_area$area_2010_square_km
abundance_and_area$Glaucus_per_sq_km <- stnd_glaucus
```

```{r}
absolute_abundance <- subset(abundance_and_area, select = c(Location, area_2010_square_km, Battus_per_sq_km,  Limenitis_per_sq_km, Polyxenes_per_sq_km, Troilus_per_sq_km, Diana_per_sq_km, Glaucus_per_sq_km) )

head(absolute_abundance)
absolute_abundance[is.na(absolute_abundance)] <- 0 ##Replace NAs with 0 
head(absolute_abundance)
```

```{r}
### Figuring out how to calculate relative abundance from absolute abundance 
check <- subset(absolute_abundance, Location == "Abbeville, South Carolina", drop = FALSE)
check <- subset(check, select = -c(Location, area_2010_square_km) )
check[1,]

total <- 0.003148755 + 0.005510322 + 0.002361567 + 0.002361567 + 0 + 0.002361567
total
 
check[1,]/total ### Example for relative abundance calculation 

##funrar package  does the same thing! Compared against my own calculate to ensure it is doing what I want it to do 
library(funrar)
# Site-species matrix
check.mat = as.matrix(check) # Absolute Abundance 
check_rel_mat = make_relative(check.mat) # Relative Abundance (divide each species count by total for that county)
```

```{r}
Location <- absolute_abundance$Location
absolute_abundance <- subset(absolute_abundance, select = -c(Location, area_2010_square_km) )
absolute_abundance_matrix <- as.matrix(absolute_abundance)
relative_abundance = make_relative(absolute_abundance_matrix)
relative_abundance <- round(relative_abundance, digits = 4)

relative_abundance <- cbind(Location, relative_abundance)
relative_abundance <- as.data.frame(relative_abundance) ## convert from matrix back into data frame format 
head(relative_abundance)[1:5,1:7]
```

```{r}
##We've calculated the relative abundance of each species in each county, now I also want to be able to compare the species richness in each county 

relative_abundance$species_richness <- rowSums(relative_abundance[-1] > 0)
head(relative_abundance) ## comparing 2,232 counties in the United States 
```
```{r}
relative_abundance$Species.Density <- density
relative_abundance <- relative_abundance[order(relative_abundance$Species.Density,decreasing=T),]
relative_abundance
```
Data Summary:
```{r}
bat ## Battus sighting counts by county
lim ##Limenitis sighting counts by county 
pol ## Polyxenes sighting counts by county 
gla ## Glaucus sighting counts by county 
dia ## Diana sighting counts by county 
tro ## Troilus sighting counts by county 

abundance_and_area ## Sighting counts and land area (km^2) & summed species density for each county 
absolute_abundance ## Sighting counts divided by land area: standardized sightings/ km^2
relative_abundance ## proportion (percent) of sightings in each county that represent each species & species richness and species density in each county
```

NEXT STEPS: 
# Now figure out how to analyze statistically! 
# package or modeling method to analyze relative abundance/ proportions?? 
# based on classic predictions about mimetic load, we would expect to see higher species richness when battus is more abundant 
  # compare species richness to the raw sighting count per county? 
  # might also be good to make a data column for the total number of sightings by county to account for frequency     vs. density differences 
# based on classic predictions of frequency dependence in mimicry, we would expect to see higher relative abundance in Battus compared to its mimic & we might see unique patterns of abundance that correlate to the degree of mimetic perfection 
  # see if relative abundance correlates to species density in each county 
  # see if relative abundance & species richness varies in the heart of Battus's range compared to the range edge     and if it varies with overall species density 
      # pull out counties where Battus is most abundant? 


